A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
clarify why future is a good solution

```{r}
set.seed(1235)
runif(1)
set.seed(1235)
runif(1)
```

```{r}
future::value(future::future(runif(1), seed = 1235))
future::value(future::future(runif(1), seed = 1235))
```

>>>>

```{r}
# reproducible but unsafe in parallel code
set.seed(1235)
runif(1)
set.seed(1235)
runif(1)
```

```{r}
# reproducible and safe in parallel code
future::value(future::future(runif(1), seed = 1235))
future::value(future::future(runif(1), seed = 1235))
```
